The Magnetorotational Instability Prefers Three Dimensions

### 2018-03-02 paper/paper.tex
added Andrew Swan to authors
some equations jazz

%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-1}

@@

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{Dedalus}
%\email[]{Your e-mail address}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{}

@@

% If in two-column mode, this environment will change to single-column
% format so that long equations can be displayed. Use
% sparingly.
%\begin{widetext}
% put long equation here
%\end{widetext}

>>>>

%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{graphicx}
% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-1}

@@

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{Dedalus}
\author{Andrew Swan}
% \email[]{Your e-mail address}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{}

@@

We solve the linearized magnetohydrodynamic equations in a rotating, shearing background. The Navier-Stokes equation is in a fairly standard form,
\begin{equation}
  \label{eq:ns}
  \frac{D \mathbf{v}}{Dt} - f \hat{z} \times \mathbf{v} + S v_x \hat{z} + \mathbf{\nabla}{p} + \nu \mathbf{\nabla} \times \mathbf{\omega} = 0,
\end{equation}
where $\omega = \mathbf{\nabla} \times \mathbf{v}$ is the vorticity and $S$ is the background shear rate. We write the induction equation in terms of the $x$ component of the magnetic field,
\begin{equation}
  \label{eq:Bx}
  \frac{D B_x}{Dt} - B_0 \partial_z v_x + \eta (\partial_y J_z - \partial_z J_y) = 0
\end{equation}
and the $x$ component of the current density,
\begin{equation}
  \label{eq:Jx}
  \frac{D J_x}{Dt} - B_0 \partial_z \omega_x + S \partial_z B_x - \eta \nabla^2 J_x = 0
\end{equation}
We explicitly enforce the divergence constraint on the incompressible velocity field $v$ and the magnetic field,
\begin{equation}
  \label{eq:divu}
  \mathbf{\nabla} \cdot \mathbf{v} = \mathbf{\nabla} \cdot \mathbf{B} = 0.
\end{equation}
We consider the behavior of the MRI in a vertically ($z$) and horizontally ($y$) periodic channel of width $L_x = \pi$. The walls at $x = \pm L_x/2$ are perfectly conducting and stress-free.

Using the \emph{Dedalus} pseudospectral framework, we solve equations~(\ref{eq:ns})(\ref{eq:Bx})(\ref{eq:divu})
\section{Results}
\label{sec:results}

\begin{figure}[h]
  \includegraphics[width=0.95\columnwidth]{growth_rates.png}
  \caption{Growth rate as a function of $k_z$ and $k_y$. The maximum growth rate is far from $k_y = 0$, indicating the MRI is most unstable in a fully three-dimensional configuration.}
  \label{fig:growth_rate}
\end{figure}
% If in two-column mode, this environment will change to single-column
% format so that long equations can be displayed. Use
% sparingly.
%\begin{widetext}
% put long equation here
%\end{widetext}
